\section*{Activities}

	\begin{subActivityList}
  \item[Talks] Daan is a gave several talks on numerous
    subjects. For a list of notable examples see
    (\url{http://dvberkel.nl/talks}).

    \item[Various Meetups] Daan frequents various Meetups, often helping out by
      providing an interesting talk to fill an available slot. Meetups where you
      can find Daan as a member include: Various Papers We Love meetups in the
      Netherlands, Various Rust meetups.

    \item[Rails Girls, Django Girls] Rails Girls and Django Girls are day long
      workshops that girls and other minority groups either Ruby on Rails or
      Python with Django. Daan volunteered on several occasions. Often during
      these workshops Daan gave an inspiring lunch talk.

    \item[Devnology] before Meetup was an established platform for organizing
      meetups Daan was a member of Devnology. Devnology was a community driven
      group of software developers that held monthly meetups. The focus was
      divided between new developments, back to school session, show-and-tell
      sessions and hackathons.

		\item[Topicus University] Daan started Topicus
                  University to create a platform for developers to
                  exchange ideas. Once a month Topicus University
                  members gather to discuss software relatede topics
                  in theire respected fields. 
		\url{https://sites.google.com/site/topicusuniversity/}.\hfill\\
	
		\item[Weblog] On \url{http://www.software-innovators.nl/}, the corporate
		weblog of Sogyo, Daan actively blogged. Daan
                communicated his ideas on software development.
		\hfill\\
		
		\item[Essay] ``Trots op mijn studie'' is a bundle of
                  essays (ISBN: 9789058750884). Daan shows in one of
                  the essays his vision on the role of mathematics in society.
		``Nieuw Archief voor Wiskunde''.		
		\hfill\\
	\end{subActivityList}
