\section*{Experience}
  \begin{workExperience}{Alliander, Arnhem}%
  {Software Developer}{\period{\moment{September}{2019}}{\present}}
        Alliander is a utility company responsible for the electric and gas network for a large part of the Netherlands.
        Alliander faces the energy transition on an already congested net. Daan lead a team that fascilitated congestion
        management by forming a gateway between Alliander and Gopacs, an energy market.
        
        \activity{Team lead} as a team lead Daan was responsible for the creation of various applications.
        Among them the GLMD-chain, Gopacs-Gateway and verification of delivery.
        Daan was also responsible for instrumenting a number of utilities that enabled teams to accelerate development
        by introducing reusable abstractions and reducing rework.
        \technics Kotlin, Spring Boot, Docker, Kubernetes, Helm, ArgoCD, Elm
        
        \activity{Knowledge sharing} Alliander was reorganized into Chapters shortly after Daan started working at Alliander.
        Daan helped shape a culture of knowledge sharing by giving talks and workshops, and fascilitating various knowledge sharing
        platforms, such as a book club, Stackoverflow for teams and Alliander Code Kata club.

        \activity{Buddy} Daan was asked to be a buddy for a trainee that started with Alliander.
        Daan was responsible for introducing the buddy to the organisation, monitoring her well-being and guiding her on her journey
        to become a proficient software developer.
  \end{workExperience}

  \begin{workExperience}{Applied University of Arnhem and Nijmegen (HAN), Arnhem}%
  {Teacher}{\period{\moment{January}{2017}}{\moment{September}{2019}}}
  The HAN provides a part-time track for software developers that want to
  broaden and deepen their knowledge of the trade. Daan was asked to join as a
  teacher. 

  \activity{Teaching Classes}
  Daan taught the following classes in various forms of the years. Object
  Oriented Software Development, Software Architecture, Algorithms, Programming
  Languages \& Paradigms.
  \technics Design Patterns, Object Oriented Programming, Complexity Analyses.

  \activity{Course Development}
  For the HAN Daan modernized the advanced software development course. This
  course focuses on Algorithms, Programming Languages \& Paradigms and Software
  Architecture.
  Daan chose to base all the example code on Elm, a Haskell like language that
  enables a succinct descriptions of data structures and algorithms.
  \technics Elm, Algorithms, Complexity Analyses, Software Architecture.

  \end{workExperience}

  \begin{workExperience}{Info Support, Veenendaal}%
  {Trainer}{\period{\moment{August}{2014}}{\moment{November}{2015}}}
  Info Support is a consultancy firm with a strong training department. Both
  internal consultants as external developer training are a part of the curriculum.

  At Info Support Daan took up the role of trainer and Java Lead. In the role of
  Java Lead Daan was responsible for tracking new developments in the language
  and deciding how to incorporate them in the curriculum and teaching to
  consultancy team. 

  \activity{Various Trainings}
  Daan gave various Java related courses ranging from Java Basics to use of
  Spring and Hibernate. Most courses run 3-days or for the entire week.
  \technics Java, Hibernate, Spring, JavaScript, Node, Scala

  \activity{Training Development}
  Daan sought out the challenge of developing new courses notable a Node course
  and a Scala course.
  \technics Node, Scala

  \end{workExperience}

  \begin{workExperience}{M-industries, Delft}%
  {Software Developer}{\period{\moment{February}{2014}}{\moment{August}{2014}}}
  M-Industries is a start up specializing in model-driven development. Daan
  contributed to M-Industries with the following activities.

  \activity{Alan}
  Alan is the main platform M-Industries develops to model software systems.
  Daan wrote some extensions to the language and help model various systems.
  \technics Node, C++, git, Alan

  \activity{Scheduling}
  One of the large customers of M-Industries is Tata steel. On of the challenges
  is treating steel products in various chemical baths. This industrial process
  is fully automated and uses heavy duty robot arms.
  Daan helped optimize part of the treatment schedule by modeling the process
  and using a constraint satisfaction solver to search optimal paths.
  \technics C++, git, Alan, gecode

  
  \end{workExperience}

	\begin{workExperience}{Luminis, Arnhem}%
	{Software Consultant}{\period{\moment{August}{2011}}{\moment{February}{2014}}}	
                Daan contributes as a software developer for Luminis
                to the following projects.
                
                \activity{NPO}
                NPO is a dutch broad casting company. NPO wanted a
                better insight into viewer ratings. The current
                solution missed usage by tablet and smartphone users.
                by analysing the logs and creating viewer events the
                missing information was provided.
                Daan contributed to this project by creating a test
                framework that could easily setup log lines and verify
                the expected results so the project could be automatic
                tested. 
                \technics Node, Redis, JavaScript, Mocha, Jake, git

                \activity{van Dijk}
                Van Dijk is a publisher of school books. Daan
                Contributed to the project by creating load and
                performance test on the webshop and aiding in the
                development of new functionality and resolution of bugs.
                \technics Groovy, Grails, JavaScript, Bamboo,
                Confluence, Jira, JMeter, svn, git

                \activity{CHARTER}
                CHARTER is a european research agreement between
                universities and business partners. Daan developed for
                Thales a Radar Tracking simulation that was used to
                test the new development tools produced by CHARTER.
                \technics Java, Bamboo, Confluence, Jira, JML, svn

                \activity{RTL 365}
                RTL is a television broadcasting company. RTL news
                releas a news app for the IPad. Daan created a content
                managment system that allowed editors to determine
                what news would be placed in the app.
                \technics o.a Groovy, Grails, Bamboo, Confluence,
                Jira, MySQL, svn
	\end{workExperience}

	\begin{workExperience}{Topicus Zorg, Deventer}%
	{Informatie architect}{\period{\moment{June}{2009}}{\moment{July}{2011}}}
                As a software developer Daan contributed to the
                following projects

		\activity{Protopics HAP}
                Protopics HAP is a information managment application
                for the healthcare provisioners. It allows the
                registration of patients and aids docters in upholding
                the national standard practices.
                Daan shaped several key components of the system,
                notably Track \& Trace and working by Protocol.
		\technics o.a. Java, Eclipse, Maven, Wicket, Hibernate, Postgres,
		Spring, SQL, Oracle, Pgadmin, Liquibase, JAX-WS, JQuery, Javascript
		
		\activity{Protopics KIS}
                Daan contributed to Protocis KIS. Protopics KIS help
                monotoring patients with complicated health problems.
		\technics o.a Java, Eclipse, Wicket, Hibernate, Spring, SQL, Oracle,
		Pgadmin, Liquibase
		
		\activity{Internship Guide}
                Daan guided several interns through their internship.
		
		\activity{Community Outreach}
                Daan was responsible for various Community Outreach
                events. Notable examples are presenting for groups of
                students and organizing a workshop for students.
		
		\activity{Framework Development}
                For Topicus Daan developed various frameworks. For
                example, by using AspectJ Daan created an hibernate
                Model for a Wicket Application.
		\technics AspectJ, Wicket, Design Patterns
	\end{workExperience}

	\begin{workExperience}{Sogyo B.V., de Bilt}%
	{Software Developer}{\period{\moment{June}{2008}}{\moment{June}{2009}}}
                Daan contributed to various projects as a software
                developer, among them are
		
		\activity{Pilot Masterclass Agile Software Ontwikkeling}
                Daan participated in a pilot for agile software
                development. The pilot entailed setting up a continous
                build environment with issue tracking, source control
                repository and a community wiki. The use case was to develop a
                library application.
		\technics o.a. Java, TestNG, Seam, JSF, Ant, svn, TeamCity, Trac, Agilo.
		
		\activity{Sogyo Interactive Graphics}
                This project entails the creating of a project
                planning module. It should aid a project manager with
                a visual way of determining which team member is
                available for a project, and for how much time.
                It explored the new JavaFX technologie by creating a
                client interface upon a java backend.
		\technics o.a. Java, JavaFX, JUnit, XML, XSLT, XPath, Tomcat, HTML,
		JavaScript, CSS, JSP, Servlets, Maven, Perl, Latex, Trac, Agilo, Flex,
		C\#, svn, Hudson, SCRUM.

	\end{workExperience}
	
	\begin{workExperience}{SumOfUs, Nijmegen}%
	{Software Developer}%
	{\period{\moment{July}{2006}}{\moment{August}{2006}}}
                Daan created a PostScript script to print hundred of
                score cards for the Nijmegen Math Competion.
		\technics o.a. Perl, Postscript.
	\end{workExperience}

	\begin{workExperience}{Ratio, Nijmegen}%
	{Software Developer}%
	{\period{\moment{January}{2001}}{\moment{January}{2005}}}
                This project had as goal to create a mathematics
                curriculum for gifted highschool studends on the web.
		\technics o.a. Perl, HTML, CSS, JavaScript.	
	\end{workExperience}
